Paper 1 Analysis

### 2015-10-18 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Move Historical_Plot to EcolEcon_2015A.Rnw. Will be used by more than one paper.

>>>>

<<Historical_Plot>>=
ggplot(histDataForGraph) + 
  geom_line(aes(x=Year, y=value, group=variable, linetype=variable, colour=variable, size=variable)) +
  facet_grid(flavor ~ Country) + 
  scale_color_manual(name = "", values=c("black", "black", "black", "gray70")) +
  scale_linetype_manual(name="", values=c(1,2,3,1)) + 
  scale_size_manual(name="", values = c(1, 0.9, 0.9, 0.6)) +
  scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12), limits=c(0.5, 12)) +
  xlab("") + 
  ylab("Indexed (1960=1)") +
  xy_theme()
@

### 2015-10-18 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Move Historical_Plot to EcolEcon_2015A.Rnw. Will be used by more than one paper.

\title{Paper 1}

@@

<<Historical_Plot, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4.0, fig.cap="Historical data.", warning=FALSE>>=
ggplot(histDataForGraph) + 
  geom_line(aes(x=Year, y=value, group=variable, linetype=variable, colour=variable, size=variable)) +
  facet_grid(flavor ~ Country) + 
  scale_color_manual(name = "", values=c("black", "black", "black", "gray70")) +
  scale_linetype_manual(name="", values=c(1,2,3,1)) + 
  scale_size_manual(name="", values = c(1, 0.9, 0.9, 0.6)) +
  scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12), limits=c(0.5, 12)) +
  xlab("") + 
  ylab("Indexed (1960=1)") +
  xy_theme()
@

@@

<<sigma_graph_3, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.82, fig.cap="Elasticities of substitution~($\\sigma$) with factors of production on the vertical facet.">>=
breaks_labels = c(0.01, 0.1, 1, 10, 100)
p <- 
  ggplot(
    AllCoeffs %>% 
      gather(type, value, matches("sigma")) %>% 
      filter(!is.na(value)) %>% 
      filter(! type %in% c("sigma", "sigma_1")) %>%
      mutate(nest = plyr::mapvalues(nest, 
                                    from=c("kle", "lek", "ekl"), 
                                    to=c("(kl)e", "(le)k", "(ek)l")),
             Model = interaction(nest, CSP, sep = " ", drop=TRUE),
             Inputs = flavor,
             type = relevelFactor(type, rev(c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2")))
             )
    ) + 
  geom_point(aes(x=value, 
                 y=type, 
                 shape = Model, 
                 fill=Model, 
                 size=Model
                 )
             ) + 
  facet_grid( Inputs ~ Country) + 
  scale_x_log10(limits = c(0.001,2000), breaks=breaks_labels, labels=breaks_labels) +
  xlab("") +
  geom_vline(xintercept = 1, color="gray50", size=0.2) +
  ylab("") +
  scale_y_discrete(labels = c(
    sigma_12 = expression(sigma[kl]),
    sigma_23 = expression(sigma[le]),
    sigma_13 = expression(sigma[ek]),
    sigma_12_3 = expression(sigma["(kl)"*e]),
    sigma_23_1 = expression(sigma["(le)"*k]),
    sigma_13_2 = expression(sigma["(ek)"*l]))
    ) +
  xy_theme() +
  theme(axis.text.y = element_text(size=12))

model_points_style_quad(p)
@

>>>>

\title{Paper 1 Analysis}

@@

<<Historical_Plot_replay, include=TRUE, echo=FALSE, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4.0, fig.cap="Historical data.", warning=FALSE>>=
<<Historical_Plot>>
@

@@
